Presentation Title

### 2017-05-29 presentation/presentation.tex
Organise into directories
Add experimental results

\usepackage{graphicx}

@@

  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{figures/trustchain-good}
  \centering
  \caption{Every node has a chain. \emph{TX block} is a six-tuple: $t_{i,j} =
    (\texttt{h}(b_{i,j-1}), h_s, h_r, s_s, s_r, m)$, one transaction results in
    two TX blocks---\emph{a pair}.}
  \end{figure}

@@

  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{figures/trustchain-bad}
  \centering
  \caption{Fork is two correctly signed TX blocks that belong to the same sender
    and has the same hash pointer but involve different receivers. Only one TX
    block may be in consensus.}
  \end{figure}

@@

  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{figures/trustchain-bad-cp}
  \centering
  \caption{CP block is a six-tuple: $c_{i,j} = (\texttt{h}(b_{i,j-1}),
    \texttt{h}(\mathcal{C}_r), h, r, p, s)$, $\mathcal{C}_r$ is the consensus
    result at round $r$, $p =$ promoter indicator, $s =$ signature.}
  \end{figure}

@@

  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{figures/trustchain-1}
  \centering
  \caption{We start in the state where $\mathcal{C}_{r - 1}$ has just been agreed but
    not yet propagated.}
  \end{figure}

@@

  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{figures/trustchain-2}
  \centering
  \caption{Nodes receive consensus result and set promoters indicator $p$, then
    send the new CP blocks to promoters of round $r$.}
  \end{figure}

@@

  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{figures/trustchain-3}
  \centering
  \caption{Transactions carry on as usual in round $r$. Note that our CP blocks
    (round $r - 1$) has not reached consensus yet.}
  \end{figure}

@@

  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{figures/trustchain-4}
  \centering
  \caption{CP blocks at round $r-1$ should be in $\mathcal{C}_r$. If we're
    lucky: $\texttt{h}(k_i || c_{i,j}) < T$, then we're responsible for
    consensus of round $r + 1$.}
  \end{figure}

@@

\begin{frame}{Experiment with 500 nodes---no gossip}
  \begin{figure}[h]
  \includegraphics[width=0.95\textwidth]{figures/consensus-500-no-gossip}
  \centering
  \end{figure}
\end{frame}

\begin{frame}{Experiment with 500 nodes---with gossip}
  \begin{figure}[h]
  \includegraphics[width=0.95\textwidth]{figures/consensus-500}
  \centering
  \end{figure}
\end{frame}

\begin{frame}{Experiment with 500 nodes---with gossip}
  \begin{block}{Conclusion}
    \begin{itemize}
      \item The number of facilitators affects the consensus latency ($O(N\log{N})$?).
      \item The transaction rate has little or not effect on the average consensus latency.
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{Planned experiments}
  \begin{itemize}
    \item Consensus latency (y-axis) vs population size (x-axis)---to
      investigate how population size impacts consensus latency.
    \item Global transaction rate vs population size---to investigate
      the scalability property.
    \item Global validation rate vs population size---to also investigate the
      scalability property.
  \end{itemize}
\end{frame}
\end{document}

>>>>

\usepackage{graphicx}
\graphicspath{{../figures/}}

@@

  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{trustchain-good}
  \centering
  \caption{Every node has a chain. \emph{TX block} is a six-tuple: $t_{i,j} =
    (\texttt{h}(b_{i,j-1}), h_s, h_r, s_s, s_r, m)$, one transaction results in
    two TX blocks---\emph{a pair}.}
  \end{figure}

@@

  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{trustchain-bad}
  \centering
  \caption{Fork is two correctly signed TX blocks that belong to the same sender
    and has the same hash pointer but involve different receivers. Only one TX
    block may be in consensus.}
  \end{figure}

@@

  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{trustchain-bad-cp}
  \centering
  \caption{CP block is a six-tuple: $c_{i,j} = (\texttt{h}(b_{i,j-1}),
    \texttt{h}(\mathcal{C}_r), h, r, p, s)$, $\mathcal{C}_r$ is the consensus
    result at round $r$, $p =$ promoter indicator, $s =$ signature.}
  \end{figure}

@@

  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{trustchain-1}
  \centering
  \caption{We start in the state where $\mathcal{C}_{r - 1}$ has just been agreed but
    not yet propagated.}
  \end{figure}

@@

  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{trustchain-2}
  \centering
  \caption{Nodes receive consensus result and set promoters indicator $p$, then
    send the new CP blocks to promoters of round $r$.}
  \end{figure}

@@

  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{trustchain-3}
  \centering
  \caption{Transactions carry on as usual in round $r$. Note that our CP blocks
    (round $r - 1$) has not reached consensus yet.}
  \end{figure}

@@

  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{trustchain-4}
  \centering
  \caption{CP blocks at round $r-1$ should be in $\mathcal{C}_r$. If we're
    lucky: $\texttt{h}(k_i || c_{i,j}) < T$, then we're responsible for
    consensus of round $r + 1$.}
  \end{figure}

@@

\begin{frame}{Consensus duration vs population size (static neighbour)}
  \begin{figure}[h]
  \includegraphics[width=0.95\textwidth]{result-normal-cons-vs-pop}
  \centering
  \end{figure}
\end{frame}

\begin{frame}{Throughput vs population size (static neighbour)}
  \begin{figure}[h]
  \includegraphics[width=0.95\textwidth]{result-normal-throughput-vs-pop}
  \centering
  \end{figure}
\end{frame}

\begin{frame}{Consensus duration vs population size (random neighbour)}
  \begin{figure}[h]
  \includegraphics[width=0.95\textwidth]{result-rand-cons-vs-pop}
  \centering
  \end{figure}
\end{frame}

\begin{frame}{Throughput vs population size (random neighbour)}
  \begin{figure}[h]
  \includegraphics[width=0.95\textwidth]{result-rand-throughput-vs-pop}
  \centering
  \end{figure}
\end{frame}

\end{document}
